---
title: "Predict the Next Word"
author: "wezhao2017"
date: "03-01-2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

Introduction
--------------

This application is trying to predict the next possible word in the sentence. To type word on the text field and up to 4 possible next words will display in below the box. 
This application was as an academic project for the Coursera Data Science Capstone. We used natural language proccessing models, n-grams model to produce the predictions.


```{r}
```

## 
```{r, echo = FALSE, warning=FALSE, message=FALSE}
library(shiny)
library(stringr)

shinyUI(
        fluidPage(
                titlePanel("Predict the Next Word"),
                sidebarLayout(
                        sidebarPanel(
                                helpText(""),
                                hr(),
                                textInput("inputText", "Enter a word to predict the next one",value = ""),
                                hr(),
                                helpText(strong("Synopsis"), 
                                         hr(),
                                         "This application try to predict the next possible word in a sentence.",
                                         hr(),
                                         "Type word(s) on the text box and up to 4 possible next words will display below."),
                                hr()
                                ),
                        mainPanel(
                                h3("Prediction Word(s) at below Box"),
                                verbatimTextOutput("prediction"),
                                 hr(),
                                h3("You enter the word(s)"),
                                strong(code(textOutput('sentence1'))),
                                br(),
                                hr()
                                )
                        )
                )
        )
```

## Thank You for Reviewing.

The shiny application is available at:https://wezhao.shinyapps.io/CapstoneApp/

The source codes (ui.R & server.R ) are available on GitHub repo at:https://github.com/wezhao2017/Capstone-final-project 